---
title: "Canonical data, history and validation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Canonical data, history and validation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

The engine consumes 68 named tables. Each historised record distinguishes
business validity from the time at which the information became known. The
official snapshot is therefore reproducible after subsequent corrections.

```{r}
library(riskweightedassets)
tables <- generate_synthetic_tables()
head(tables$run_config[c("config_key", "config_value")])
head(tables$exposure_lot[c("record_id", "business_key", "valid_from",
                           "known_from", "is_official")])
```

Workbook validation returns structured messages rather than prose-only logs.

```{r, eval=FALSE}
report <- validate_dataset("path/to/dataset")
issues <- as.data.frame(report)
subset(issues, severity == "ERROR")
```

Technical validation cannot decide institution-specific scope, permissions or
legal interpretation. Those remain governed inputs.
