---
title: "Getting started with riskweightedassets"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with riskweightedassets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

The package provides an auditable R workflow for canonical risk-weighted asset
data. Start by inspecting the two bundled profiles.

```{r}
library(riskweightedassets)
list_reference_profiles()
```

Generate native R tables without writing files.

```{r}
tables <- generate_synthetic_tables(bank_profile = "KSA_BANK")
length(tables)
names(tables)[1:12]
```

A full calculation is intentionally not executed while building this vignette
because it calculates applied and fully-loaded views. Run it interactively:

```{r, eval=FALSE}
result <- calculate_tables(tables)
print(result)
unlist(result$metrics[c("RWEA_KSA", "TREA", "CET1_RATIO")])
```

For a spreadsheet workflow, write only below a controlled caller-owned path:

```{r, eval=FALSE}
dataset <- generate_synthetic_dataset(
  file.path(tempdir(), "rwa-runs"), bank_profile = "KSA_BANK"
)
validate_dataset(dataset)
result <- calculate_dataset(dataset)
```

The data is synthetic, and the package is not regulatory or legal advice.
