---
title: "Methodology, controls and result interpretation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Methodology, controls and result interpretation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

The pipeline calculates credit SA and IRB, CRM, CCR/SFT/CCP, CVA,
securitisation, settlement, large exposures, market and operational risk,
capital constraints, IRRBB/CSRBB and ICAAP. A Standardised shadow view supplies
the output-floor denominator. Applied and fully-loaded rule sets use the same
official bitemporal snapshot.

```{r, eval=FALSE}
library(riskweightedassets)
result <- calculate_tables(generate_synthetic_tables())
names(result$results)
result$controls
```

Every result table adds run, formula-version, reporting date, knowledge time,
rule set, view and official-status metadata. A successful reference result has
no validation errors and every reconciliation control passes. Production use
still requires independent legal, data, model and reporting governance.
